Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2014-11-06 draft_lm1.tex
improved introduction

%%%% Revised up to here

Secondly, there are a larger number of asymptomatic cases in 
any epidemic, which nevertheless acquire immunity. It is estimated that for 
every case reported, 10-20 are not seen by health authorities (personnal 
communication).
Thirdly, under-reporting is a serious issue in Brazil. 
Duarte and Fran\c{c}a\cite{duarte_data_2006}, estimated 
the sensitivity of dengue reporting for hospitalized patients in 
Belo-Horizonte, Brazil to be of 63\%, 
meaning that aproximately 37\% of the suspected dengue cases go unreported.  
Lastly, demography and migrations affect the number of susceptible in ways which 
are not easy to determine.

>>>>

Various challenges exist to assess the attack rate of a dengue epidemic. One of 
them is that there are a large number of asymptomatic cases in any epidemic, 
which nevertheless acquire immunity. It is estimated that for 
every case reported, 10-20 are not seen by health authorities (personnal 
communication).
Thirdly, under-reporting is a serious issue in Brazil. 
Duarte and Fran\c{c}a\cite{duarte_data_2006}, estimated 
the sensitivity of dengue reporting for hospitalized patients in 
Belo-Horizonte, Brazil to be of 63\%, 
meaning that aproximately 37\% of the suspected dengue cases go unreported.  
Lastly, demography and migrations affect the number of susceptible in ways which 
are not easy to determine.
